---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nmmBtm

<!-- badges: start -->
<!-- badges: end -->

The goal of nmmBtm is to help researchers analyse the data from www.nomoremarking.com

## Installation

You can install the the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("NoMoreMarking/nmmBtm")
```
## Examples

Using the decisions data downloaded from www.nomoremarking.com you can fit your own btm model using the following:

```{r decisions}
require(nmmBtm)
data("decisions")
mdl <- nmmBtm::btmModel(decisions)
print(summary(mdl))
```

You can estimate judge infit using the following:

```{r infit}
data("decisions")
mdl <- btmModel(decisions)
probs <- mdl$probs
judge.infit <- btm_fit_2(probs,decisions)
print(judge.infit)
```

You can convert theta values to scaled scores:

```{r scaled}
data("decisions")
mdl <- btmModel(decisions)
scaledScores <- scaleThetas(mdl$effects, 20, 0)
print(scaledScores)
```

You can simulate a new set of model parameters from the initial model estimates:

```{r simulate}
data("decisions")
sims <- btmSimulate(decisions, NULL, 2)
print(head(sims))
```

You can bootstrap sample the decisions file to produce new estimates:

```{r bootstrap-sample}
data("decisions")
bootstrapped <- btmBootstrap(decisions, 3, size = 0.8, replace = FALSE)
print(head(bootstrapped))
```
